### 2018-06-20 pubs/itp-2018/sections/proof-reconstruction/conjunct.tex
[ paper ] all proofs have been removed.
First review to the conjunct fule text

The \conjunct rule extracts from a conjunction one of its conjuncts.
This rule is a generalization of the projection rules for the
conjunction connective as the following \TSTP excerpt shows.

\begin{myexamplenum}\hspace{10cm}

\begin{verbatim}
  fof(p₁, p ∧ q ∧ (r ∨ ¬ p), ...
  fof(p₂, q, inf(conjunct, p₁)).
  fof(p₃, r ∨ ¬ p, inf(conjunct, p₁)).
\end{verbatim}

In the first formula, $p ∧ q ∧ (r ∨ ¬ p)$, we find a left-associative
conjunction named \verb!p₁!. The \conjunct rule extracts $q$ from the
\verb!p₁! using a left projection (∧-proj₁) follow by a right
projection (∧-proj₂). After, the \conjunct rule extracts $r ∨ ¬ p$ by
using a right projection on \verb!p₁!.

@@

\begin{proof}\hspace{10cm}
\begin{itemize}
\item[∙] Case $φ ≡ ψ$. $Γ ⊢ \fconjunct~φ~ψ$ normalizes to $Γ ⊢ ψ$.
Then, we get the desire conclusion by applying the $\fsubst$ lemma.
\item[∙] Case $φ ≡ φ₁ ∧ φ₂$. If we can get $ψ ≡ \fconjunct~φ_{i}~ψ$ for some $i = 1,\ 2$, then,

\begin{equation*}
  \begin{bprooftree}
  \AxiomC{$Γ ⊢ φ₁ ∧ φ₂$}
  \RightLabel{∧-proj$_{i}$}
  \UnaryInfC{$Γ ⊢ φ_{i}$}
  \RightLabel{by~ind.~hyp.}
  \UnaryInfC{$Γ ⊢ \fconjunct~φ_{i}~ψ$}
  \AxiomC{$ψ ≡ \fconjunct~φ_{i}~ψ$}
  \RightLabel{\fsubst}
  \BinaryInfC{$Γ ⊢ ψ$}
  \end{bprooftree}
\end{equation*}
\item[∙] Otherwise, the last case follows from the hypothesis.
\end{itemize}
\end{proof}

>>>>

The \conjunct rule extracts from a conjunction one of its conjuncts.
This rule is a generalization of the projection rules for the
conjunction connective.
See in  as the following \TSTP excerpt shows.

\begin{myexamplenum}

In Fig.~\ref{complete-metis-example}, we see in line~\ref{line20} how we get $ ¬
p ∨ q$ from the formula in line~\ref{line19}, $(¬ p ∨ q) ∧ (¬ q ∨ p)$, by means
of the \conjunct rule, that in this case acts as a left projection (∧-proj₁).

@@
